---
title: "Assignment-1_MIS 64060"
author: "Asher John"
date: "9/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is first assignment of the course. The data in the assignment has been used from the built-in data in R Studio. The following tables and plots show the data about car speeds and the distance cars take to stop at those speeds. This data was collected in 1920s hence the slow speeds. The speeds are mph and the distance is in feet. The summary shows the summary of the data. The scatter plot shows the relationship between the speed and the stopping distance. 

```{r cars}
summary(cars)
```

## Scatter Plot
The scatter plot shows the relationship between variables `speed` and `distance` .


```{r, echo=FALSE}
plot(cars)
```



## Transformed Data

I also transformed the data into log10.




```{r}
(log10(cars))

```




## Scatter Plot of the Transformed Data


I also plotted the transformed data. 



```{r}
plot(log10(cars))
```



