---
title: "Assignment-3"
author: "Asher John"
date: "10/18/2021"
output:
  html_document: default
  pdf_document: default
---

## A. Please find the output below.
## B. The probability of this customer accepting the loan is 84/892 i.e. 0.094 or 9.4%.
## C. Please find the output below
## answers for D all answers are approximations
## i.     0.29 or 29%
## ii.    0.62 or 62%
## iii.   0.096 or 9.6%
## iv.    0.298 or 29.8%
## v.     0.599 or 59.9%
## vi.    0.904 or 90.4%

## E. Use the quantities computed above to compute the naive Bayes probability of P(Loan = 1 | CC = 1, Online = 1). Answer is given below:

## (P(CC = 1 | Loan = 1)*P(Online = 1 | Loan = 1)*P(Loan = 1))/(p(CC=1)*P(Online=1))    

## (.2916*.6215*.096)/(.601*.2973) =  0.0973712

## F. The value obtained in E is 0.097 or 9.7% probability while value obtained in B is 0.094 or  9.4% probabilty of P(Loan = 1 | CC = 1, Online = 1).The value obtained in B is more accurate.

## G. The entry wher CC = 1, Personal Loan = 1 and Online = 1 is needed for computing P(Loan = 1 | CC = 1, Online = 1). The value in E is .0973 but the valuse after examining the model output on training data is .096, i.e. is little different. 



```{r}
library(caret)
library(dplyr)
library(e1071)

bank <- read.csv("UniversalBank.csv")
str(bank)
bank$Personal.Loan = as.factor(bank$Personal.Loan)
bank$Online = as.factor(bank$Online)
bank$CreditCard = as.factor(bank$CreditCard)


```

## Partitioning the data

```{r}
selected.var <- c(10,13,14)

set.seed(13)

Valid_Index <- createDataPartition(bank$Personal.Loan, p=0.4, list=FALSE)

Valid_bank <- bank[Valid_Index, selected.var]
  
Training_bank <- bank[-Valid_Index, selected.var]

summary(Valid_bank)

summary(Training_bank)

```

## B. Creating a Pivot Table   
 
```{r}
library(reshape2)

melt.bank <- melt(Training_bank,id=c("CreditCard","Personal.Loan"),variable= "Online")
pivot.bank <- dcast(melt.bank,CreditCard+Personal.Loan~Online)
pivot.bank
ftable(pivot.bank, row.vars = 1:2, col.vars = 3)

prop.table(ftable(pivot.bank, row.vars = 1:2, col.vars = 3), margin = 1)

train.nb <- naiveBayes(Personal.Loan ~ ., data = Training_bank)

train.nb

```

## C. Create two separate pivot tables for the training data. One will have Loan (rows) as a function of Online (columns) and the other will have Loan (rows) as a function of CC.

```{r}
melt.bank1 <-  melt(Training_bank,id= "Personal.Loan", variable= "Online")
pivot.bank1 <- dcast(melt.bank1, Personal.Loan~Online)
pivot.bank1
table(Training_bank[, c(1,2)] )
prop.table(table(Training_bank[, c(1,2)] ), margin = 1)

melt.bank2 <-  melt(Training_bank,id= "Personal.Loan", variable= "CreditCard")
pivot.bank2 <- dcast(melt.bank2, Personal.Loan~CreditCard)
pivot.bank2
table(Training_bank[, c(1,3)] )
prop.table(table(Training_bank[, c(1,3)] ), margin = 1)

table(Training_bank[, c(1)])
prop.table(table(Training_bank[, c(1)]))

``` 





## G. Which of the entries in this table are needed for computing P(Loan = 1 | CC = 1, Online = 1)? Run naive Bayes on the data. Examine the model output on training data, and find the entry that corresponds to P(Loan = 1 | CC = 1, Online = 1). Compare this to the number you obtained in (E).

```{r}
bank.nb <- naiveBayes(Personal.Loan ~ ., data = bank[, c(10,13,14)])
bank.nb


```

